\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Userless Classificaton for the Yelp Dataset Challenge}

### 2015-12-12 paper/article_2.tex
changes to the paper + abstract

We planned on building latent features from the text reviews which would depict the cat- egories of the business. To put it in a nutshell, we would like to build from the text reviews of an entry a vector representation which carries local geometry information. Once we built the document-term matrix containing the words count of the reviews for each business (the reviews are aggregated over each restaurant), we could simply use a matrix factorisation on the counts . To be able to interpret the latent features as topics, we could use a Non-negative matrix factorization (the possible negative features in the SVD cannot stand for cluster as- signement). A finer result can be reached with the use of a generative probabilistic model, that’s why we chosed the latent dirichlet allocation. The LDA uses a Dirichlet prior on the words distribution over the topics and on the topics distribution over the document which will gives them more freedom than the deterministic approach of the NMF.

@@

\lettrine[nindent=0em,lines=1]{T}he classification system in Yelp is manual. When the owner of a business creates a page for his restaurant or bar, he is asked to enter a certain number of attributes or "tags". Yelp users can then alter or even add some new tags based on their experiences. As part of the Yelp Data Set Challenge Round 6, we decided to tackle the issue of classification with ultimate objective to be able to create an automatised method to classify venues, based on the information contained on the business' web page and most importantly the written reviews from Yelpers. \\

This project can be divided in two parts, the first on feature extraction and the second on classification and clustering. In more details, we applied various dimensionality reduction methods such as Latent Dirichlet Allocation (LDA) or Non-negative Matrix Factorisation (NMF) to embed the reviews into a geometrical space. We then decided to compare both supervised approaches such as Multinomial Regression and unsupervised approaches, using the Walktrap algorithm, to the problem of classification on the Yelp dataset.
%------------------------------------------------

\section{Data}

@@

We would like to also make a general comment about the Online Variational algorithm. We noticed that the OVI algorithm is extremely sensitive to the hyperparametrisation, i.e the batch size $S$, the forgetfullness parameter $\kappa$ and the early iterations weith parameter $\tau$. This was also noted by Tamara Broderick, Nicholas Boyd, Andre Wibisono and Ashia C. Wilson in their paper\cite{svi}. In addition to validating the number of topics, validating over these parameters was crucial to obtain valuable resutls.\\

We now present two different approaches to answer the question of classification using supervised and unsupervised machine learning.\\

@@

Once the feature have been extracted, we can apply supervised learning methods to classify the Yelp restaurants considering the category labels as output. Several approaches are possible to solve this multi-labels classiffication task depending on the nature and patterns of the features.

@@

The features are divided into two main parts: on one hand, the topics assignements extracted from the reviews with the LDA and on the other hand, the properties provided by Yelp. Pre-processing the latter part provided a 198 dimensional vector. These features contain both numerical values (rating, space coordinates, number of reviews, customer check-in...) and categorical ones which we converted into indicator variables.\\

Given our numerical features, many different discriminative and generative models could be appllied on our data. Nonetheless, the indicator features are sparse and the data are really noisy. We need to consider a penalized or aggregated model to reduce overfitting.\\

We chose a one-vs-all approach to tackle this multi-labels task where we build one binary classifier for each label. We then assign to the entries the labels predicted by each model. The goal is here to explore how the different models perform and to tune them to come up with the best estimator. We developped our own l2 penalized logistic regression and used sklearn for the other models.

@@

We decided to reduce the dimension of the dataset before applying our model. We used it only on the customer check-ins counts to embed them in an euclidean space. We chose to project them because they already shared a common structure. Then, the combination of the embedded features with the latent features provided by the reviews is more consistent. We chose to apply it while keeping \textbf{95\%} of the variance which reduces the dimension from \textbf{168} to \textbf{19}.

@@

Here we provide the different results we obtained from our models. We ran one-vs-one classifiers for the 10 different labels which are the most represented in the Las Vegas restaurants. Then we evaluated for each classifier its accuracy and averaged them to get the evaluation metric printed in the table. We tested them on three different kinds of features provided by the reviews depending on the method used to build them. Then we ran each model on the PCA projection and on the raw data. We provided for comparaison the baseline model where we do not assign any label. This result is really high because of the skewness of the considered sample, among the 10 categories considered for 3822 restaurants the most represented (Fast Food) contains 553 entries and the least (American New) 280 entries.

@@

The first learning of this comparative study is the differences between each kind of feature. The models built with the GS features seems to outperform on average the two other which perform similarly to each other. These results are not surprising as the variationnal inference learns the closest model to the underlying one in terms of KL divergence. With the Gibbs sampling approach, we approximate the true underlying distribution at each iteration to refine our estimator. As a result, the latter method is by nature better to find the best model as long as it has enough iteration to converge and there actually exists an underlying mixture models. Nevertheless, the OVI remains a good proxy with regard to its time execution (53s against 50min for the Gibbs Sampler).\\

Then, if we compare the models to each other. The support vector machine performs poorly, the linear version was even closer to the baseline. This confirms that the data are not linearly separable and even their projection by the rbf function used in sklearn library (gamma function) is quite impossible to separate. The logistic regression performs better under the l1 penalization because of our sparse feature. Lastly, the random forest managed to reduce the common overfitting of the decision trees while aggregating them and provides on the PCA projection a very good estimator.\\

We plotted here the ROC curves of the Random forest for the 10 classes considered. The ranking of the area under the curve is almost the same that the descending ranking by number of positive elements for each classe.This shows that the more positive elements we have the better classifies the model. Nonethelless, trying to learn the model on a smaller and more balanced train set for the classes with a low number of positive elements does not improve the classification accuracy.

@@

TODO: analysis on the ROC curves

@@

Once we found a sufficiantly good estimator, we can investigate the weights it assigns to each feature. This could provide an answer to two important questions: \textit{Are the feature extracted from the reviews more relevant than the one provided by Yelp to classify the restaurants by category? Among the features extracted by the review, can we identify for each category one or several highly discriminative features?} Moreover, we can compare the performance of the two different LDA we used.\\

We answer these questions with a comparative study on four specific categories (Fast Food, Pizza, Nightlife and Bars) with a Random Forest on four kinds of features, depending on the type of LDA used and the reduction with a PCA. The results with the features built with an NMF are similar to those with the OVI. We used the measure provided by scikit learn to evaluate the importance of the features. It is defined as the total decrease in node impurity averaged over all trees of the ensemble.

@@

First, considering the results for the OVI features, we observe that some properties provided by Yelp are discriminative for our classification. For example, the attribute \textit{Good for Kids} helps to sort the Bars and the Nightlife categories which is not surprising. The Fast Food may be the restaurants with the largest number of reviews as they have the largest number of customers, the model confirms this with the high weight on the \textit{reviews\_count}. This is also a cheap restaurant, hence the importance of the price range. As a result, it is worth considering the features provided by Yelp as they help discriminate the entries.\\

Second, for the categories Pizza with the features extracted by the OVI we observe a discriminative feature which matchs the one about Pizza provided in the figure 3. Then, for the same LDA method, there is no discriminative feature for the other categories. Now, if we consider the results for the GS features, each category has a highly discriminative feature. Moreover, if we look at the most common words for each of these topics in the figure 10, we naturally understand their importance in the classification. This result confirms our analysis on the models. The Gibbs sampling method provides a finer topic distribution over the documents (here it is a labels distribution over the restaurants).

Lastly, it is worth noticing the effect of the PCA on the importance of the features. For both the OVI and the GS, if we consider the category pizza, the results with the PCA are much more clear-cut. The weight of the most important feature and its difference with those of the other features are higher. We can explain this because the projection gives more structure to the data and reduces the noise.\\

This part was about confronting our data to supervised methods to grasp their patterns and also coming up with a good classification. We provided empirical results to confirm the difference between the two most common LDA methods and proved that with the Gibbs sampling, the LDA can be really efficient to find the underlying topics of a set of documents, being much butter than a matrix factorization method. Related to our problem, it shows us that the features contain some information, but the LDA features remain more important to find the labels of a restaurant.

>>>>

Our objective is to improve the categorization system of the Yelp businesses using machine learning techniques. To achieve our goal, we extract significant information out of the text reviews posted on Yelp using our own coded-up Latent Dirichlet Allocation (LDA) using Online Variational Inference, and benchmark it with an LDA using Gibbs Sampling and Non Negative Matrix Factorisation. We then present two methods for classifying restaurants. We first resorted to a supervised approach with a multinomial logistic regression on  the text reviews combined with characteristic features of businesses - such as localisations, prices, customer type or check-in data. The second approach is unsupervised, using the Walktrap Algorithm, a community detection algorithm on network of restaurant. If the different feature extraction methods (LDA, NMF) performed differently for the supervised and unsupervised approach, we observed some very promising results. The results could be used as the first step to an automated categorization system on the Yelp website.

@@

\lettrine[nindent=0em,lines=1]{T}he classification system in Yelp is manual. When the owner of a business creates a page for his restaurant or bar, he is asked to enter a certain number of attributes or "tags". Yelp users can then alter or even add some new tags based on their experiences. As part of the Yelp Data Set Challenge Round 6, we decided to tackle the issue of classification with ultimate objective to be able to create an automatised method to classify venues, based on the information contained on the business' web page and most importantly the written reviews from Yelpers.

\noindent This project can be divided in two parts, the first on feature extraction and the second on classification and clustering. In more details, we applied various dimensionality reduction methods such as Latent Dirichlet Allocation (LDA) or Non-negative Matrix Factorisation (NMF) to embed the reviews into a geometrical space. We then decided to compare both supervised approaches such as Multinomial Regression and unsupervised approaches, using the Walktrap algorithm, to the problem of classification on the Yelp dataset.
%------------------------------------------------
\columnbreak
\section{Data}

@@

\noindent We would like to also make a general comment about the Online Variational algorithm. We noticed that the OVI algorithm is extremely sensitive to the hyperparametrisation, i.e the batch size $S$, the forgetfullness parameter $\kappa$ and the early iterations weith parameter $\tau$. This was also noted by Tamara Broderick, Nicholas Boyd, Andre Wibisono and Ashia C. Wilson in their paper\cite{svi}. In addition to validating the number of topics, validating over these parameters was crucial to obtain valuable resutls.\\

\noindent We now present two different approaches to answer the question of classification using supervised and unsupervised machine learning.\\

@@

Once the features have been extracted, we can apply supervised learning methods to classify the Yelp restaurants considering the category labels as output. Several approaches are possible to solve this multi-label classiffication task depending on the nature and patterns of the features.

@@

\noindent The features are divided into two main parts: on one hand, the topics assignements extracted from the reviews with the LDA and on the other hand, the properties provided by Yelp. Pre-processing the latter part provided a 198 dimensional vector. These features contained both numerical values (rating, space coordinates, number of reviews, customer check-in...) and categorical ones which we converted into indicator variables.\\

\noindent Given our numerical features, many different discriminative and generative models could be appllied on our data. Nonetheless, the indicator features are sparse and the data are really noisy. We therefore needed to consider a penalized or aggregated model to reduce overfitting.\\

\noindent We chose a one-vs-all approach to tackle this multi-label task, and built one binary classifier for each label. We then assign to the entries the labels predicted by each model. The goal is here to explore how the different models perform and to tune them to come up with the best estimator. We developped our own L2 penalized logistic regression and used sklearn for the other models.

@@

\noindent We decided to reduce the dimension of the dataset before fitting our model. As the high-dimensionality is largely due to the customer check-in counts and as they share a common structure, we decided to project them in an euclidean space. The combination of the embedded features with the latent features provided by the reviews is more consistent. We apply a principal component analysis (PCA) while keeping \textbf{95\%} of the variance which reduces the dimension from \textbf{168} to \textbf{19}.

@@

\noindent Here we provide the different results we obtained from our models. We ran one-vs-one classifiers for the 10 different labels which are the most represented in the Las Vegas restaurants. Then we evaluated for each classifier its accuracy and averaged them to get the evaluation metric printed in the table. We tested them on three different kinds of features provided by the reviews depending on the method used to build them. Then we ran each model on the PCA projection and on the raw data. We also show for comparaison the baseline model where we do not assign any label. This result is really high because of the skewness of the considered sample, among the 10 categories considered for 3822 restaurants the most represented (Fast Food) contains 553 entries and the least (American New) 280 entries.

@@

\noindent The first outcome of this comparative study is the differences between each feature extraction method. The model built with the GS features seems to outperform on average the other two, which perform similarly to each other. These results are not surprising as the variationnal inference learns the closest model to the underlying one in terms of KL divergence. With the Gibbs sampling approach, we approximate the true underlying distribution at each iteration to refine our estimator. As a result, the latter method is by nature better to find the best model as long as it has enough iteration to converge and there actually exists an underlying mixture models. Nevertheless, the OVI remains a good proxy with regard to its time execution (53s against 50min for the Gibbs Sampler).\\

\noindent If we then compare the models to each other, we see that the support vector machine performs poorly and that the linear version was even closer to the baseline. This confirms that the data is not linearly separable and even their projection by the rbf function used in sklearn library (gamma function) is quite impossible to separate. The logistic regression performs better under the l1 penalization because of the sparsity of our features. Lastly, the random forest managed to reduce the common overfitting of the decision trees while aggregating them and provides on the PCA projection a very good estimator.\\

\noindent We plotted here the ROC curves of the Random forest for the 10 classes considered. The ranking with respect to the area under the curve is very close to the one induced by the number of positive elements for each class.This shows that the more positive elements we have, the better the model actually performs. Nonetheless, trying to learn the model on a smaller and more balanced train set for the classes with a low number of positive elements does not improve the classification accuracy.

@@

@@

\noindent Once we found a sufficiantly good estimator, we investigated the weights it assigned to each feature. This provided an answer to two important questions: \textit{Are the feature extracted from the reviews more relevant than the one provided by Yelp to classify the restaurants by category? Among the features extracted by the review, can we identify for each category one or several highly discriminative features?} Moreover, we can compare the performance of the two different LDA we used.\\

\noindent We answer these questions with a comparative study on four specific categories (Fast Food, Pizza, Nightlife and Bars) with a Random Forest on four kinds of features, depending on the type of LDA used and the reduction with PCA. The results with the features built with an NMF are similar to those with the OVI. We used the measure provided by scikit learn to evaluate the importance of the features. It is defined as the total decrease in node impurity averaged over all trees of the ensemble.

@@

\noindent First, considering the results for the OVI features, we observe that some properties provided by Yelp are discriminative for our classification. For example, the attribute \textit{Good for Kids} helps to sort the Bars and the Nightlife categories which is not surprising. The Fast Food may be the restaurants with the largest number of reviews as they have the largest number of customers, the model confirms this with the high weight on the \textit{reviews\_count}. This is also a cheap restaurant, hence the importance of the price range. As a result, it is worth considering the features provided by Yelp as they help discriminate the entries.\\

\noindent Second, for the Pizza category with the features extracted by the OVI we observe a discriminative feature which matchs the one about Pizza provided in the figure 3. Then, for the same LDA method, there is no discriminative feature for the other categories. Now, if we consider the results for the GS features, each category has a highly discriminative feature. Moreover, if we look at the most common words for each of these topics in the figure 10, we naturally understand their importance in the classification. This result confirms our analysis on the models. The Gibbs sampling method provides a finer topic distribution over the documents (here it is a label distribution over the restaurants).

\noindent Lastly, it is worth noticing the effect of the PCA on the feature importance. For both the OVI and the GS, if we look back at the Pizza category, the results with the PCA are much more clear-cut. The weight of the most important feature and its difference with those of the other features are higher. We can explain this by the fact that the projection gave more structure to the data and reduces the noise.\\

\noindent This part was about confronting our data to supervised methods to grasp their patterns and also coming up with a good classification. We provided empirical results to confirm the difference between the two common LDA methods and proved that with the Gibbs sampling, the LDA can be really efficient at finding the underlying topics on a set of documents.  It also proved that it performed much butter than a matrix factorization method. Related to our problem, it showed us that if numerical features provided by Yelp contained some information, the LDA features remained much more important when looking to find the labels of a restaurant.
